---
title: "Report A Modelling Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Undertake An Exploratory Modelling Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Note: **This vignette uses fake data** - it is for illustrative purposes only and should not be used to inform decision making.

```{r message=FALSE, warning=FALSE}
library(ready4)
library(ready4show)
library(ready4use)
library(scorz)
library(specific)
```

## Import data

We start by ingesting our data. As this example uses EQ-5D data, we import a `ScorzEuroQol5` object that was created using the steps described in [this vignette from the scorz pacakge](https://ready4-dev.github.io/scorz/articles/V_02.html).

```{r message=FALSE}
X <- ready4use::Ready4useRepos(gh_repo_1L_chr = "ready4-dev/scorz", 
                               gh_tag_1L_chr = "Documentation_0.0") %>%
    ingest(fls_to_ingest_chr = "ymh_ScorzEuroQol5",
         metadata_1L_lgl = F)
```

```{r}
X <- renewSlot(X,
          "instrument_short_nm_1L_chr",
          "EQ-5D")
# X@itm_prefix_1L_chr
# X@instrument_nm_1L_chr
```
```{r}
Y <- SpecificModels(a_YouthvarsProfile = procureSlot(X,"a_YouthvarsProfile"), # Metamorphose
                    paths_chr = tempdir()) 
```

## Specify parameters

In preparation for exploring our dataset, we need to declare a set of model parameters in a `SpecificParameters` object. 

```{r}
Y <- renewSlot(Y,
               "b_SpecificParameters",
               SpecificParameters(depnt_var_nm_1L_chr = X@total_wtd_var_nm_1L_chr,
                                  depnt_var_min_max_dbl = c(-1,1),
                                  candidate_predrs_chr = c("K10_int","Psych_well_int"),
                                  candidate_covars_chr = c("d_sex_birth_s", "d_age",  "d_sexual_ori_s", "d_studying_working"),
                                  candidate_mdls_lup = get_cndt_mdls(mdl_short_nms_chr = c("OLS_NTF","OLS_CLL","GLM_GSN_LOG")),
                                  control_ls = list(adapt_delta = 0.99),
                                  folds_1L_int = 10L,
                                  max_mdl_runs_1L_int = 300L,
                                  seed_1L_int = 1234L))
```

```{r}
Y <- renewSlot(Y, 
               "b_SpecificParameters@predictors_lup", 
               short_name_chr = procureSlot(Y,
                                            "b_SpecificParameters@candidate_predrs_chr"),
               long_name_chr = c("Kessler Psychological Distress - 10 Item Total Score",
                                 "Overall Wellbeing Measure (Winefield et al. 2012)"),
               min_val_dbl = c(10,18),
               max_val_dbl = c(50,90),
               class_chr = "integer",
               increment_dbl = 1,
               class_fn_chr = "as.integer",
               mdl_scaling_dbl = 0.01,
               covariate_lgl = F)
```

## Specify metadata about the manuscript to be authored

```{r}
Z <- ready4show::Ready4showSynopsis(authors_r3 = ready4show::authors_tb,
                                    coi_1L_chr = "None declared.",
                                    digits_int = c(3L,3L),
                                    ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
                                    funding_1L_chr = "The study was funded by Generous Benefactor.",
                                    institutes_r3 = ready4show::institutes_tb,
                                    interval_chr = "three months",
                                    keywords_chr = c("entirely","fake","do", "not","cite"),
                                    outp_formats_chr = c("PDF","PDF"),
                                    title_1L_chr = "A hypothetical study using fake data")
```
```{r}
Z <- renewSlot(Z,
               "correspondences_r3",
               old_nms_chr = c("PHQ9", "GAD7"),
               new_nms_chr = c("PHQ-9", "GAD-7"))
```


```{r}
A <- ready4use::Ready4useRepos(dv_nm_1L_chr = "fakes",
                          dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/GW7ZKC")
```

```{r}
ds_descvs_ls <- make_ds_descvs_ls(candidate_predrs_chr =  Y@b_SpecificParameters@candidate_predrs_chr,
                                  candidate_covar_nms_chr = Y@b_SpecificParameters@candidate_covars_chr,
                                  cohort_descv_var_nms_chr = c("d_age", "Gender", 
                                                               "d_relation_s","d_sexual_ori_s", 
                                                               "Region", "d_studying_working"), # Add to Params
                                  dictionary_tb = Y@a_YouthvarsProfile@a_Ready4useDyad@dictionary_r3, 
                                  id_var_nm_1L_chr = Y@a_YouthvarsProfile@id_var_nm_1L_chr, 
                                  is_fake_1L_lgl = T,
                                  msrmnt_date_var_nm_1L_chr = "data_collection_dtm",
                                  round_var_nm_1L_chr = Y@a_YouthvarsProfile@timepoint_var_nm_1L_chr, 
                                  round_vals_chr = Y@a_YouthvarsProfile@timepoint_vals_chr,
                                  maui_item_pfx_1L_chr = X@itm_prefix_1L_chr, 
                                  utl_wtd_var_nm_1L_chr = X@total_wtd_var_nm_1L_chr,
                                  utl_unwtd_var_nm_1L_chr = X@total_unwtd_var_nm_1L_chr) # Manufacture
```
```{r}
header_yaml_args_ls <- ready4show::make_header_yaml_args_ls(authors_tb = Z@authors_r3,
                                                institutes_tb = Z@institutes_r3,
                                                title_1L_chr = Z@title_1L_chr,
                                                keywords_chr = Z@keywords_chr)
```

```{r}
maui_params_ls <- make_maui_params_ls(maui_domains_pfxs_1L_chr = X@itm_prefix_1L_chr,
                                      maui_itm_short_nms_chr = X@itm_labels_chr,
                                      maui_scoring_fn = function(data_tb,
                                             maui_item_pfx_1L_chr,
                                             id_var_nm_1L_chr, 
                                             utl_wtd_var_nm_1L_chr,
                                             utl_unwtd_var_nm_1L_chr){
                    require(eq5d)
                    data_tb %>% 
                      dplyr::rename_with(~stringr::str_replace(.x,maui_item_pfx_1L_chr,""),
                                         dplyr::starts_with(maui_item_pfx_1L_chr)) %>%
                      dplyr::mutate(`:=`(!!rlang::sym(utl_wtd_var_nm_1L_chr), 
                                         eq5d::eq5d(., country="UK", version = "5L", type = "CW"))) %>%
                      dplyr::rename_with(~paste0(maui_item_pfx_1L_chr,.x),c("MO","SC","UA","PD","AD")) %>%
                      dplyr::mutate(`:=`(!!rlang::sym(utl_unwtd_var_nm_1L_chr),                                          rowSums(dplyr::across(dplyr::starts_with(maui_item_pfx_1L_chr))))) %>%
                      dplyr::filter(!is.na(!!rlang::sym(utl_unwtd_var_nm_1L_chr)))
                    },
                    short_and_long_nm = c("EQ-5D",
                                          "EuroQol - Five Dimension"))
```

```{r}
output_format_ls <- ready4show::make_output_format_ls(manuscript_outp_1L_chr = Z@outp_formats_chr[1],
                                          manuscript_digits_1L_int = Z@digits_int[1],
                                          supplementary_outp_1L_chr = ifelse(length(Z@outp_formats_chr)>1,Z@outp_formats_chr[2],Z@outp_formats_chr[1]),
                                          supplementary_digits_1L_int = ifelse(length(Z@digits_int)>1,Z@digits_int[2],Z@digits_int[1]))
```
```{r}
# scndry_anlys_params_ls <- make_scndry_anlys_params(candidate_predrs_chr = c("SOFAS"),
#                                                    prefd_covars_chr = NA_character_)
```

```{r}
input_params_ls <- make_input_params(Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb,
                                     control_ls = Y@b_SpecificParameters@control_ls,
                                     ds_descvs_ls = ds_descvs_ls,
                                     dv_ds_nm_and_url_chr = c(A@dv_nm_1L_chr, 
                                                              A@dv_ds_nm_1L_chr), 
                                     header_yaml_args_ls = header_yaml_args_ls,
                                     maui_params_ls = maui_params_ls,
                                     output_format_ls = output_format_ls,
                                     predictors_lup = Y@b_SpecificParameters@predictors_lup,
                                     prefd_covars_chr = NA_character_#,
                                     #prefd_mdl_types_chr = c("OLS_CLL","GLM_GSN_LOG"),
                                     #scndry_anlys_params_ls = scndry_anlys_params_ls
                                     )#
```

```{r}
write_analyses(input_params_ls)
```

