---
title: "Report A Modelling Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Undertake An Exploratory Modelling Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Note: **This vignette uses fake data** - it is for illustrative purposes only and should not be used to inform decision making.

```{r message=FALSE, warning=FALSE}
library(ready4)
library(ready4show)
library(ready4use)
library(scorz)
library(specific)
```

## Import data

We start by ingesting our data. As this example uses EQ-5D data, we import a `ScorzEuroQol5` object that was created using the steps described in [this vignette from the scorz pacakge](https://ready4-dev.github.io/scorz/articles/V_02.html).

```{r message=FALSE}
X <- ready4use::Ready4useRepos(gh_repo_1L_chr = "ready4-dev/scorz", 
                               gh_tag_1L_chr = "Documentation_0.0") %>%
    ingest(fls_to_ingest_chr = "ymh_ScorzEuroQol5",
         metadata_1L_lgl = F)
```

```{r}
X <- renewSlot(X,
               "instrument_short_nm_1L_chr",
               "EQ-5D")
# X@itm_prefix_1L_chr
# X@instrument_nm_1L_chr
```
```{r}
Y <- SpecificModels(a_YouthvarsProfile = procureSlot(X,"a_YouthvarsProfile"), # Metamorphose
                    paths_chr = tempdir()) 
```

## Specify parameters

In preparation for exploring our dataset, we need to declare a set of model parameters in a `SpecificParameters` object. 

```{r}
Y <- renewSlot(Y,
               "b_SpecificParameters",
               SpecificParameters(depnt_var_nm_1L_chr = X@total_wtd_var_nm_1L_chr,
                                  depnt_var_min_max_dbl = c(-1,1),
                                  candidate_predrs_chr = c("K10_int","Psych_well_int"),
                                  candidate_covars_chr = c("d_sex_birth_s", "d_age",  "d_sexual_ori_s", "d_studying_working"),
                                  candidate_mdls_lup = get_cndt_mdls(mdl_short_nms_chr = c("OLS_NTF","OLS_CLL","GLM_GSN_LOG")),
                                  control_ls = list(adapt_delta = 0.99),
                                  folds_1L_int = 10L,
                                  max_mdl_runs_1L_int = 300L,
                                  seed_1L_int = 1234L))
```

```{r}
Y <- renewSlot(Y, 
               "b_SpecificParameters@predictors_lup", 
               short_name_chr = procureSlot(Y,
                                            "b_SpecificParameters@candidate_predrs_chr"),
               long_name_chr = c("Kessler Psychological Distress - 10 Item Total Score",
                                 "Overall Wellbeing Measure (Winefield et al. 2012)"),
               min_val_dbl = c(10,18),
               max_val_dbl = c(50,90),
               class_chr = "integer",
               increment_dbl = 1,
               class_fn_chr = "as.integer",
               mdl_scaling_dbl = 0.01,
               covariate_lgl = F)
```

## Specify metadata about the manuscript to be authored

```{r}
Z <- ready4show::Ready4showSynopsis(authors_r3 = ready4show::authors_tb,
                                    coi_1L_chr = "None declared.",
                                    digits_int = c(3L,3L),
                                    ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
                                    funding_1L_chr = "The study was funded by Generous Benefactor.",
                                    institutes_r3 = ready4show::institutes_tb,
                                    interval_chr = "three months",
                                    keywords_chr = c("entirely","fake","do", "not","cite"),
                                    outp_formats_chr = c("PDF","PDF"),
                                    title_1L_chr = "A hypothetical study using fake data")
```
```{r}
Z <- renewSlot(Z,
               "correspondences_r3",
               old_nms_chr = c("PHQ9", "GAD7"),
               new_nms_chr = c("PHQ-9", "GAD-7"))
```

```{r}
A <- ready4use::Ready4useRepos(dv_nm_1L_chr = "fakes",
                          dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/GW7ZKC")
```

```{r}
# Y <- renew(Y,
#            c("OLS_CLL","GLM_GSN_LOG"),
#            what_1L_chr = "prefd_mdls")
```
```{r}
# Y <- renew(Y,
#            NA_character_,
#            what_1L_chr = "prefd_covars")
```
```{r }
set.seed(procureSlot(Y,
                     "b_SpecificParameters@seed_1L_int"))
session_data_ls <- sessionInfo() # Add to results?
```
```{r}
cohort_descv_var_nms_chr = c("d_age", "Gender","d_relation_s","d_sexual_ori_s", 
                             "Region", "d_studying_working")
fake_1L_lgl = T 
itm_labels_chr = X@itm_labels_chr 
itm_prefix_1L_chr = X@itm_prefix_1L_chr 
msrmnt_date_var_nm_1L_chr = "data_collection_dtm" 
paths_ls = NULL # UPDATED BELOW
total_unwtd_var_nm_1L_chr = X@total_unwtd_var_nm_1L_chr #
```
```{r }
## AUTHOR METHOD
if(is.null(reference_1L_int)){
transform_paths_ls <- list(fn = transform_paths_ls_for_scndry,
                          args_ls = list(reference_1L_int = reference_1L_int)) # FOR SECONDARY
}else{
  transform_paths_ls <- NULL
}
path_params_ls <- make_path_params_ls() 
path_params_ls$use_fake_data_1L_lgl <- fake_1L_lgl
paths_ls <- path_params_ls %>%
  ready4show::make_paths_ls(depth_1L_int = ifelse(is.null(transform_paths_ls),
                                                  1,
                                                  2))
if(!is.null(transform_paths_ls)){
  paths_ls <- rlang::exec(transform_paths_ls$fn,
                          paths_ls,
                        !!!transform_paths_ls$args_ls)
}
paths_ls <- ready4show::write_all_outp_dirs(paths_ls = paths_ls)
```
```{r }
# Ratify method
Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb <- Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb %>% 
  youthvars::add_interval_var(id_var_nm_1L_chr = Y@a_YouthvarsProfile@id_var_nm_1L_chr,
                              msrmnt_date_var_nm_1L_chr = ifelse(!is.null(msrmnt_date_var_nm_1L_chr), 
                                                                 ## CHANGE REF - ADD TO MODULE
                                                                 msrmnt_date_var_nm_1L_chr,
                                                                 "d_interview_date")) %>%
  youthvars::add_participation_var(id_var_nm_1L_chr = Y@a_YouthvarsProfile@id_var_nm_1L_chr,
                                   fup_round_nbr_1L_int = length( Y@a_YouthvarsProfile@timepoint_vals_chr))
if(is.na(Y@a_YouthvarsProfile@participation_var_1L_chr)){
 Y@a_YouthvarsProfile@participation_var_1L_chr <- "participation"
}
Y@a_YouthvarsProfile@a_Ready4useDyad@dictionary_r3 <- Y@a_YouthvarsProfile@a_Ready4useDyad@dictionary_r3 %>%
  ready4::renew(var_nm_chr = c("bl_date_dtm", 
                               "interval_dbl", 
                               Y@a_YouthvarsProfile@participation_var_1L_chr), 
                var_ctg_chr = c("Temporal", 
                                "Temporal", 
                                "Temporal"), 
                var_desc_chr = c("Date of baseline assessment", 
                                 "Interval between baseline and follow-up assessments", 
                                 "Rounds participated in"), 
                var_type_chr = c("date", 
                                 "interval", 
                                 "character"))
Y <- renewSlot(Y,
               "a_YouthvarsProfile@a_Ready4useDyad",
               type_1L_chr = "label")
Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb <- Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb %>%
  transform_mdl_vars_with_clss(predictors_lup = Y@b_SpecificParameters@predictors_lup,
                               depnt_var_nm_1L_chr = Y@b_SpecificParameters@depnt_var_nm_1L_chr#,
                               #prototype_lup = params_ls$prototype_lup, # Supplied as arg?
                               #class_fn_1L_chr = "as.numeric" # Supplied as arg?
                               )
```

## SAVE COPY OF INPUT DATA (WRITE_INPUTS_FOR_MAIN ANALYSIS) ???
```{r}
## TRANSFORMATION FN HAD BEEN HERE
## DONT DELETE - NEEDED FOR REAL DATA
```



<!-- DESCRIPTIVES  -- START -->

```{r}
## MANUFACTURE
if(what_1L_chr %in% c("ds_descvs_ls","ds_smry_ls"))
object_xx <- make_ds_descvs_ls(candidate_predrs_chr =  Y@b_SpecificParameters@candidate_predrs_chr,
                                  candidate_covar_nms_chr = Y@b_SpecificParameters@candidate_covars_chr,
                                  cohort_descv_var_nms_chr = descv_var_nms_chr, # Add to Params
                                  dictionary_tb = Y@a_YouthvarsProfile@a_Ready4useDyad@dictionary_r3, 
                                  id_var_nm_1L_chr = Y@a_YouthvarsProfile@id_var_nm_1L_chr, 
                                  is_fake_1L_lgl = fake_1L_lgl,
                                  msrmnt_date_var_nm_1L_chr = msrmnt_date_var_nm_1L_chr,
                                  round_var_nm_1L_chr = Y@a_YouthvarsProfile@timepoint_var_nm_1L_chr, 
                                  round_vals_chr = Y@a_YouthvarsProfile@timepoint_vals_chr,
                                  utl_wtd_var_nm_1L_chr = Y@b_SpecificParameters@depnt_var_nm_1L_chr,
                               maui_item_pfx_1L_chr = itm_prefix_1L_chr, ### ADD 1
                                  utl_unwtd_var_nm_1L_chr = total_unwtd_var_nm_1L_chr) ### ADD 2

if(what_1L_chr == ("ds_smry_ls"))
  object_xx <- object_xx %>%
  make_analysis_ds_smry_ls(candidate_covar_nms_chr = Y@b_SpecificParameters@candidate_covars_chr,
                           predictors_lup = Y@b_SpecificParameters@predictors_lup)
if(what_1L_chr == "mdl_smry_ls"){
  if(is.na(Y@b_SpecificParameters@candidate_mdls_chr)){
  mdl_types_chr <- NULL
}else{
  mdl_types_chr <- Y@b_SpecificParameters@candidate_mdls_chr
}
if(is.na(Y@b_SpecificParameters@candidate_mdl_pfcs_chr)){
  choose_from_pfx_chr <- NULL
}else{
  choose_from_pfx_chr <- Y@b_SpecificParameters@candidate_mdl_pfcs_chr
}
object_xx <- make_mdl_smry_ls(mdl_types_lup = Y@b_SpecificParameters@candidate_mdls_lup,
                             mdl_types_chr = mdl_types_chr,
                             choose_from_pfx_chr = choose_from_pfx_chr,
                             folds_1L_int = Y@b_SpecificParameters@folds_1L_int,
                             max_nbr_of_boruta_mdl_runs_int = Y@b_SpecificParameters@max_mdl_runs_1L_int)
}


  
  #params_ls$mdl_smry_ls
```

```{r, results='hide', message=FALSE, warning=FALSE, fig.show='hide'}
# Author Method
descv_tbl_ls <- youthvars::write_descv_tbls(Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb,
                                            ds_descvs_ls = ds_descvs_ls,
                                            predictors_lup = Y@b_SpecificParameters@predictors_lup,
                                            descv_outp_dir_1L_chr = paths_ls$descv_outp_dir_1L_chr,
                                            nbr_of_digits_1L_int = Z@digits_int[1])
descv_plts_paths_ls <- youthvars::write_descv_plots(Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb,
                                                    ds_descvs_ls = ds_descvs_ls,
                                                    descv_outp_dir_1L_chr = paths_ls$descv_outp_dir_1L_chr, ### PATHS LS REQUIRED
                                                    lbl_nms_chr = itm_labels_chr, ## ADD 3
                                                    maui_domains_pfxs_1L_chr = itm_prefix_1L_chr) ## ADD 1

```

<!-- DESCRIPTIVES  -- END-->


Compare model types using most correlated predictor.

```{r message=FALSE, results='hide', warning=FALSE}
cmprsns_ls <- write_mdl_cmprsn(scored_data_tb = data_tb,
                                ds_smry_ls = ds_smry_ls,
                                mdl_smry_ls = mdl_smry_ls,
                                output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                seed_1L_int = params_ls$seed_1L_int)

```

Select preferred model types.

```{r echo = !is.null(params_ls$prefd_mdl_types_chr), eval= !is.null(params_ls$prefd_mdl_types_chr), message=FALSE, results='hide', warning=FALSE}
if(!is.null(params_ls$prefd_mdl_types_chr)){
  cmprsns_ls$mdl_smry_ls$prefd_mdl_types_chr <- params_ls$prefd_mdl_types_chr
}
```

Compare candidate predictors and covariates using most preferred model type.

```{r message=FALSE, results='hide', warning=FALSE}
cmprsns_ls <- write_predr_and_covars_cmprsn(scored_data_tb = data_tb,
                                           bl_tb = cmprsns_ls$bl_tb,
                                           ds_smry_ls = cmprsns_ls$ds_smry_ls,
                                           mdl_smry_ls  = cmprsns_ls$mdl_smry_ls,
                                           output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                           seed_1L_int = params_ls$seed_1L_int)
```

`r ifelse(!is.null(params_ls$prefd_covars_chr),"Specify the covariates to include.","")`

```{r echo = !is.null(params_ls$prefd_covars_chr), eval = !is.null(params_ls$prefd_covars_chr), message=FALSE, results='hide', warning=FALSE}
if(!is.null(params_ls$prefd_covars_chr)){
  cmprsns_ls$mdl_smry_ls$prefd_covars_chr <- params_ls$prefd_covars_chr
}
```

Compare selected models with selected predictors and selected covariates.

```{r message=FALSE, results='hide', warning=FALSE, fig.show ='hide'}
outp_smry_ls <- write_mdls_with_covars_cmprsn(scored_data_tb = data_tb,
                                           bl_tb = cmprsns_ls$bl_tb,
                                           ds_smry_ls = cmprsns_ls$ds_smry_ls,
                                           mdl_smry_ls = cmprsns_ls$mdl_smry_ls,
                                           output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                           seed_1L_int = params_ls$seed_1L_int,
                                           session_data_ls = session_data_ls)
```

```{r results='hide', message=FALSE, warning=FALSE}
outp_smry_ls <- write_ts_mdls_from_alg_outp(outp_smry_ls,
                                                 utl_min_val_1L_dbl = params_ls$utl_min_val_1L_dbl,
                                                 predictors_lup = params_ls$predictors_lup,
                                                 backend_1L_chr = "cmdstanr",
                                                 new_dir_nm_1L_chr = "F_TS_Mdls",
                                                 iters_1L_int = params_ls$iters_1L_int, 
                                                 prior_ls = params_ls$prior_ls, 
                                                 control_ls = params_ls$control_ls)
```
```{r results='hide', message=FALSE, warning=FALSE}
saveRDS(outp_smry_ls, 
        paste0(outp_smry_ls$path_to_write_to_1L_chr, "/I_ALL_OUTPUT_.RDS"))
```

```{r}
# write_analyses(input_params_ls) # Secondary analyses component

```


```{r}
# header_yaml_args_ls <- ready4show::make_header_yaml_args_ls(authors_tb = Z@authors_r3,
#                                                 institutes_tb = Z@institutes_r3,
#                                                 title_1L_chr = Z@title_1L_chr,
#                                                 keywords_chr = Z@keywords_chr)
```

```{r}
# maui_params_ls <- make_maui_params_ls(maui_domains_pfxs_1L_chr = X@itm_prefix_1L_chr,
#                                       maui_itm_short_nms_chr = X@itm_labels_chr,
#                                       maui_scoring_fn = NULL)
```

```{r}
# output_format_ls <- ready4show::make_output_format_ls(manuscript_outp_1L_chr = Z@outp_formats_chr[1],
#                                           manuscript_digits_1L_int = Z@digits_int[1],
#                                           supplementary_outp_1L_chr = ifelse(length(Z@outp_formats_chr)>1,Z@outp_formats_chr[2],Z@outp_formats_chr[1]),
#                                           supplementary_digits_1L_int = ifelse(length(Z@digits_int)>1,Z@digits_int[2],Z@digits_int[1]))
```
```{r}
# scndry_anlys_params_ls <- make_scndry_anlys_params(candidate_predrs_chr = c("SOFAS"),
#                                                    prefd_covars_chr = NA_character_)
```

```{r}
# input_params_ls <- make_input_params(Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb,
#                                      control_ls = Y@b_SpecificParameters@control_ls,
#                                      ds_descvs_ls = ds_descvs_ls,
#                                      dv_ds_nm_and_url_chr = c(A@dv_nm_1L_chr, 
#                                                               A@dv_ds_nm_1L_chr), 
#                                      header_yaml_args_ls = header_yaml_args_ls,
#                                      maui_params_ls = maui_params_ls,
#                                      output_format_ls = output_format_ls,
#                                      predictors_lup = Y@b_SpecificParameters@predictors_lup,
#                                      prefd_covars_chr = procure(Y,what = "prefd_covars"),
#                                      prefd_mdl_types_chr = procure(Y,what = "prefd_mdls")#,
#                                      #scndry_anlys_params_ls = scndry_anlys_params_ls
#                                      )#
```
