---
title: "Report A Modelling Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Undertake An Exploratory Modelling Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Note: **This vignette uses fake data** - it is for illustrative purposes only and should not be used to inform decision making.

```{r message=FALSE, warning=FALSE}
library(ready4)
library(ready4show)
library(ready4use)
library(scorz)
library(specific)
```

## Import data

We start by ingesting our data. As this example uses EQ-5D data, we import a `ScorzEuroQol5` object that was created using the steps described in [this vignette from the scorz pacakge](https://ready4-dev.github.io/scorz/articles/V_02.html).

```{r message=FALSE}
X <- ready4use::Ready4useRepos(gh_repo_1L_chr = "ready4-dev/scorz", 
                               gh_tag_1L_chr = "Documentation_0.0") %>%
    ingest(fls_to_ingest_chr = "ymh_ScorzEuroQol5",
         metadata_1L_lgl = F)
```

```{r}
# X <- renewSlot(X,
#                "instrument_short_nm_1L_chr",
#                "EQ-5D")
# X@itm_prefix_1L_chr
# X@instrument_nm_1L_chr
```
```{r}
paths_chr <- tempdir()
# Metamorphose
Y <- SpecificModels(a_YouthvarsProfile = procureSlot(X,"a_YouthvarsProfile"), 
                    b_SpecificParameters = SpecificParameters(depnt_var_nm_1L_chr = X@total_wtd_var_nm_1L_chr,
                                                              itm_labels_chr = X@itm_labels_chr,
                                  itm_prefix_1L_chr = X@itm_prefix_1L_chr,
                                  total_unwtd_var_nm_1L_chr = X@total_unwtd_var_nm_1L_chr),
                    paths_chr = paths_chr) 
```

## Specify parameters

In preparation for exploring our dataset, we need to declare a set of model parameters in a `SpecificParameters` object. 

```{r}
Y <- renewSlot(Y,
               "b_SpecificParameters",
               procureSlot(Y,
                           "b_SpecificParameters") %>%
                 renewSlot("depnt_var_min_max_dbl",
                           c(-1,1)) %>%
                 renewSlot("candidate_predrs_chr",
                           c("K10_int","Psych_well_int")) %>%
                 renewSlot("candidate_covars_chr",
                           c("d_sex_birth_s", "d_age",  "d_sexual_ori_s", "d_studying_working")) %>%
                 renewSlot("candidate_mdls_lup",
                           get_cndt_mdls(mdl_short_nms_chr = c("OLS_NTF","OLS_CLL","GLM_GSN_LOG"))) %>%
                 renewSlot("descv_var_nms_chr",
                           c("d_age","Gender","d_relation_s",
                                                               "d_sexual_ori_s", "Region",
                                                               "d_studying_working")) %>% 
                 renewSlot("control_ls",
                           list(adapt_delta = 0.99)) %>%
                 renewSlot("fake_1L_lgl",
                           T) %>%
                 renewSlot("folds_1L_int",
                           10L) %>%
                 renewSlot("max_mdl_runs_1L_int",
                           300L) %>%
                  renewSlot("msrmnt_date_var_nm_1L_chr",
                           "data_collection_dtm") %>%
                 renewSlot("seed_1L_int",
                           1234L)) 
```

```{r}
Y <- renewSlot(Y, 
               "b_SpecificParameters@predictors_lup", 
               short_name_chr = procureSlot(Y,
                                            "b_SpecificParameters@candidate_predrs_chr"),
               long_name_chr = c("Kessler Psychological Distress - 10 Item Total Score",
                                 "Overall Wellbeing Measure (Winefield et al. 2012)"),
               min_val_dbl = c(10,18),
               max_val_dbl = c(50,90),
               class_chr = "integer",
               increment_dbl = 1,
               class_fn_chr = "as.integer",
               mdl_scaling_dbl = 0.01,
               covariate_lgl = F)
```

## Specify metadata about the manuscript to be authored
<!-- Move this to later -->
```{r}
Z <- ready4show::Ready4showSynopsis(authors_r3 = ready4show::authors_tb,
                                    coi_1L_chr = "None declared.",
                                    digits_int = c(3L,3L),
                                    ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
                                    funding_1L_chr = "The study was funded by Generous Benefactor.",
                                    institutes_r3 = ready4show::institutes_tb,
                                    interval_chr = "three months",
                                    keywords_chr = c("entirely","fake","do", "not","cite"),
                                    outp_formats_chr = c("PDF","PDF"),
                                    title_1L_chr = "A hypothetical study using fake data")
```
```{r}
Z <- renewSlot(Z,
               "correspondences_r3",
               old_nms_chr = c("PHQ9", "GAD7"),
               new_nms_chr = c("PHQ-9", "GAD-7"))
```

```{r}
A <- ready4use::Ready4useRepos(dv_nm_1L_chr = "fakes",
                          dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/GW7ZKC")
```

```{r}
# Y <- renew(Y,
#            c("OLS_CLL","GLM_GSN_LOG"),
#            what_1L_chr = "prefd_mdls")
```
```{r}
# Y <- renew(Y,
#            NA_character_,
#            what_1L_chr = "prefd_covars")
```
```{r }
# set.seed(procureSlot(Y,
#                      "b_SpecificParameters@seed_1L_int"))
session_data_ls <- sessionInfo() # Add to results?
```

```{r}
Y <- ratify(Y)
Y <- author(Y,
            what_1L_chr = "workspace")
```

## SAVE COPY OF INPUT DATA (WRITE_INPUTS_FOR_MAIN ANALYSIS) ???
```{r}
## TRANSFORMATION FN HAD BEEN HERE
## DONT DELETE - NEEDED FOR REAL DATA
```

```{r, results='hide', message=FALSE, warning=FALSE, fig.show='hide'}
Y <- author(Y,
            what_1L_chr = "descriptives",
            digits_1L_int = Z@digits_int[1])

```

Compare model types using most correlated predictor.

```{r message=FALSE, results='hide', warning=FALSE}
cmprsns_ls <- write_mdl_cmprsn(scored_data_tb = Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb,
                                ds_smry_ls = manufacture(Y,
                                                                        what_1L_chr = "ds_smry_ls"),
                                mdl_smry_ls = manufacture(Y,
                                                                        what_1L_chr = "mdl_smry_ls"),
                                output_data_dir_1L_chr = Y@b_SpecificParameters@paths_ls$output_data_dir_1L_chr,
                                seed_1L_int = Y@b_SpecificParameters@seed_1L_int)

```

Select preferred model types.

```{r, message=FALSE, results='hide', warning=FALSE}
prefd_mdl_types_chr <- NULL
if(!is.null(prefd_mdl_types_chr)){
  cmprsns_ls$mdl_smry_ls$prefd_mdl_types_chr <- prefd_mdl_types_chr
}
```

Compare candidate predictors and covariates using most preferred model type.

```{r message=FALSE, results='hide', warning=FALSE}
cmprsns_ls <- write_predr_and_covars_cmprsn(scored_data_tb = data_tb,
                                           bl_tb = cmprsns_ls$bl_tb,
                                           ds_smry_ls = cmprsns_ls$ds_smry_ls,
                                           mdl_smry_ls  = cmprsns_ls$mdl_smry_ls,
                                           output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                           seed_1L_int = params_ls$seed_1L_int)
```

`r ifelse(!is.null(params_ls$prefd_covars_chr),"Specify the covariates to include.","")`

```{r echo = !is.null(params_ls$prefd_covars_chr), eval = !is.null(params_ls$prefd_covars_chr), message=FALSE, results='hide', warning=FALSE}
if(!is.null(params_ls$prefd_covars_chr)){
  cmprsns_ls$mdl_smry_ls$prefd_covars_chr <- params_ls$prefd_covars_chr
}
```

Compare selected models with selected predictors and selected covariates.

```{r message=FALSE, results='hide', warning=FALSE, fig.show ='hide'}
outp_smry_ls <- write_mdls_with_covars_cmprsn(scored_data_tb = data_tb,
                                           bl_tb = cmprsns_ls$bl_tb,
                                           ds_smry_ls = cmprsns_ls$ds_smry_ls,
                                           mdl_smry_ls = cmprsns_ls$mdl_smry_ls,
                                           output_data_dir_1L_chr = paths_ls$output_data_dir_1L_chr,
                                           seed_1L_int = params_ls$seed_1L_int,
                                           session_data_ls = session_data_ls)
```

```{r results='hide', message=FALSE, warning=FALSE}
outp_smry_ls <- write_ts_mdls_from_alg_outp(outp_smry_ls,
                                                 utl_min_val_1L_dbl = params_ls$utl_min_val_1L_dbl,
                                                 predictors_lup = params_ls$predictors_lup,
                                                 backend_1L_chr = "cmdstanr",
                                                 new_dir_nm_1L_chr = "F_TS_Mdls",
                                                 iters_1L_int = params_ls$iters_1L_int, 
                                                 prior_ls = params_ls$prior_ls, 
                                                 control_ls = params_ls$control_ls)
```
```{r results='hide', message=FALSE, warning=FALSE}
saveRDS(outp_smry_ls, 
        paste0(outp_smry_ls$path_to_write_to_1L_chr, "/I_ALL_OUTPUT_.RDS"))
```

```{r}
# write_analyses(input_params_ls) # Secondary analyses component

```


```{r}
# header_yaml_args_ls <- ready4show::make_header_yaml_args_ls(authors_tb = Z@authors_r3,
#                                                 institutes_tb = Z@institutes_r3,
#                                                 title_1L_chr = Z@title_1L_chr,
#                                                 keywords_chr = Z@keywords_chr)
```

```{r}
# maui_params_ls <- make_maui_params_ls(maui_domains_pfxs_1L_chr = X@itm_prefix_1L_chr,
#                                       maui_itm_short_nms_chr = X@itm_labels_chr,
#                                       maui_scoring_fn = NULL)
```

```{r}
# output_format_ls <- ready4show::make_output_format_ls(manuscript_outp_1L_chr = Z@outp_formats_chr[1],
#                                           manuscript_digits_1L_int = Z@digits_int[1],
#                                           supplementary_outp_1L_chr = ifelse(length(Z@outp_formats_chr)>1,Z@outp_formats_chr[2],Z@outp_formats_chr[1]),
#                                           supplementary_digits_1L_int = ifelse(length(Z@digits_int)>1,Z@digits_int[2],Z@digits_int[1]))
```
```{r}
# scndry_anlys_params_ls <- make_scndry_anlys_params(candidate_predrs_chr = c("SOFAS"),
#                                                    prefd_covars_chr = NA_character_)
```

```{r}
# input_params_ls <- make_input_params(Y@a_YouthvarsProfile@a_Ready4useDyad@ds_tb,
#                                      control_ls = Y@b_SpecificParameters@control_ls,
#                                      ds_descvs_ls = ds_descvs_ls,
#                                      dv_ds_nm_and_url_chr = c(A@dv_nm_1L_chr, 
#                                                               A@dv_ds_nm_1L_chr), 
#                                      header_yaml_args_ls = header_yaml_args_ls,
#                                      maui_params_ls = maui_params_ls,
#                                      output_format_ls = output_format_ls,
#                                      predictors_lup = Y@b_SpecificParameters@predictors_lup,
#                                      prefd_covars_chr = procure(Y,what = "prefd_covars"),
#                                      prefd_mdl_types_chr = procure(Y,what = "prefd_mdls")#,
#                                      #scndry_anlys_params_ls = scndry_anlys_params_ls
#                                      )#
```
