---
title: "Report A Modelling Analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Undertake An Exploratory Modelling Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## NEW GAME
```{r}
library(ready4)
library(specific)
```

```{r}
X <- ready4use::Ready4useRepos(gh_repo_1L_chr = "ready4-dev/specific", 
                          gh_tag_1L_chr = "Documentation_0.0") %>%
                         ingest(fls_to_ingest_chr = "eq5d_ttu_SpecificMixed",
                                metadata_1L_lgl = F)
```

## Specify metadata about the manuscript to be authored
<!-- Move this to later -->
```{r}
A <- ready4use::Ready4useRepos(dv_nm_1L_chr = "fakes",
                               dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/GW7ZKC")
```
```{r}
Z <- ready4show::Ready4showSynopsis(authors_r3 = ready4show::authors_tb,
                                    coi_1L_chr = "None declared.",
                                    digits_int = c(3L,3L),
                                    ethics_1L_chr = "The study was reviewed and granted approval by Awesome University's Human Research Ethics Committee (1111111.1).",
                                    funding_1L_chr = "The study was funded by Generous Benefactor.",
                                    institutes_r3 = ready4show::institutes_tb,
                                    interval_chr = "three months",
                                    keywords_chr = c("entirely","fake","do", "not","cite"),
                                    outp_formats_chr = c("PDF","PDF"),
                                    title_1L_chr = "A hypothetical study using fake data")
```
```{r}
Z <- renewSlot(Z,
               "correspondences_r3",
               old_nms_chr = c("PHQ9", "GAD7"),
               new_nms_chr = c("PHQ-9", "GAD-7"))
```

### Report

```{r}
Z <- renewSlot(Z,
               "a_Ready4showPaths@outp_data_dir_1L_chr",
               X@b_SpecificParameters@paths_ls$output_data_dir_1L_chr %>% stringi::stri_replace_last_regex("/Output",""))#X@paths_chr
Z <- renewSlot(Z,
               "rmd_fl_nms_ls",
               ready4show::make_rmd_fl_nms_ls("Lngl_Mdls_HTML",
                                              pdf_fl_nm_1L_chr = "Lngl_Mdls_PDF",
                                              word_fl_nm_1L_chr = "Lngl_Mdls_Word")
)
# procureSlot(Z,
#             "a_Ready4showPaths@ms_mkdn_dir_1L_chr")
# procureSlot(Z,
#             "a_Ready4showPaths@ms_dir_1L_chr")
```
```{r}
authorData_Ready4showSynopsis(Z,
           tmpl_url_1L_chr = "https://github.com/ready4-dev/ttu_mdl_ctlg",
           tmpl_version_1_L_chr = "0.0.9.1")
```
```{r}
authorReport(Z)
# Make child class of Z that includes results
# Add reference to results slot of X/Z in template
# Change relative paths
# Trial relocation of child RMD
# Remove output.yml from template
# 
```

### XXXXX
```{r}
## MANUFACTURE_SpecificMixed
input_params_ls <- manufacture(X, ## FIX
                               a_Ready4useRepos = A,
                               scndry_anlys_params_ls = NULL,
                               what_1L_chr = "input_params_ls")
```
```{r}
input_params_ls <- write_mdl_smry_rprt(input_params_ls,
                                       use_shareable_mdls_1L_lgl = T)
```

### Share
```{r}
X <- renew_SpecificMixed(X,
                         a_Ready4useRepos = A)
```




```{r}
outp_smry_ls$
```



Note: **This vignette uses fake data** - it is for illustrative purposes only and should not be used to inform decision making.

```{r message=FALSE, warning=FALSE}
library(ready4)
library(ready4show)
library(ready4use)
library(scorz)
library(specific)
```

## Import data

We start by ingesting our data. As this example uses EQ-5D data, we import a `ScorzEuroQol5` module (created using the steps described in [this vignette from the scorz pacakge](https://ready4-dev.github.io/scorz/articles/V_02.html))    into a `SpecificConverter` Module.

```{r message=FALSE}
X <- SpecificConverter(a_ScorzProfile = ready4use::Ready4useRepos(gh_repo_1L_chr = "ready4-dev/scorz", 
                                                 gh_tag_1L_chr = "Documentation_0.0") %>%
                         ingest(fls_to_ingest_chr = "ymh_ScorzEuroQol5",
                                metadata_1L_lgl = F))
```

```{r}
# X <- renewSlot(X,
#                "instrument_short_nm_1L_chr",
#                "EQ-5D")
# X@itm_prefix_1L_chr
# X@instrument_nm_1L_chr
```
```{r}
Y <- metamorphose(X,
                  paths_chr = tempdir())
```

## Specify parameters

In preparation for exploring our dataset, we need to declare a set of model parameters in a `SpecificParameters` object. 

```{r}
Y <- renewSlot(Y,
               "b_SpecificParameters",
               procureSlot(Y,
                           "b_SpecificParameters") %>%
                 renewSlot("depnt_var_min_max_dbl",
                           c(-1,1)) %>% ## Check min/max
                 renewSlot("candidate_predrs_chr",
                           c("K10_int","Psych_well_int")) %>%
                 renewSlot("candidate_covars_chr",
                           c("d_sex_birth_s", "d_age",  "d_sexual_ori_s", "d_studying_working")) %>%
                 renewSlot("candidate_mdls_lup",
                           get_cndt_mdls(mdl_short_nms_chr = c("OLS_NTF","OLS_CLL","GLM_GSN_LOG"))) %>%
                 renewSlot("descv_var_nms_chr",
                           c("d_age","Gender","d_relation_s",
                                                               "d_sexual_ori_s", "Region",
                                                               "d_studying_working")) %>% 
                 renewSlot("control_ls",
                           list(adapt_delta = 0.99)) %>%
                 renewSlot("fake_1L_lgl",
                           T) %>%
                 renewSlot("folds_1L_int",
                           10L) %>%
                 renewSlot("max_mdl_runs_1L_int",
                           300L) %>%
                  renewSlot("msrmnt_date_var_nm_1L_chr",
                           "data_collection_dtm") %>%
                 renewSlot("seed_1L_int",
                           1234L)) 
```

```{r}
Y <- renewSlot(Y, 
               "b_SpecificParameters@predictors_lup", 
               short_name_chr = procureSlot(Y,
                                            "b_SpecificParameters@candidate_predrs_chr"),
               long_name_chr = c("Kessler Psychological Distress - 10 Item Total Score",
                                 "Overall Wellbeing Measure (Winefield et al. 2012)"),
               min_val_dbl = c(10,18),
               max_val_dbl = c(50,90),
               class_chr = "integer",
               increment_dbl = 1,
               class_fn_chr = "as.integer",
               mdl_scaling_dbl = 0.01,
               covariate_lgl = F)
```


```{r}
# Y <- renew(Y,
#            c("OLS_CLL","GLM_GSN_LOG"),
#            what_1L_chr = "prefd_mdls")
```
```{r}
# Y <- renew(Y,
#            NA_character_,
#            what_1L_chr = "prefd_covars")
```
```{r }
# set.seed(procureSlot(Y,
#                      "b_SpecificParameters@seed_1L_int"))
session_data_ls <- sessionInfo() # Add to results?
```

```{r}
Y <- ratify(Y)
Y <- author(Y,
            what_1L_chr = "workspace")
```

## SAVE COPY OF INPUT DATA (WRITE_INPUTS_FOR_MAIN ANALYSIS) ???
```{r}
## TRANSFORMATION FN HAD BEEN HERE
## DONT DELETE - NEEDED FOR REAL DATA
```

```{r, results='hide', message=FALSE, warning=FALSE, fig.show='hide'}
Y <- author(Y,
            what_1L_chr = "descriptives",
            digits_1L_int = Z@digits_int[1])

```



```{r results='hide', message=FALSE, warning=FALSE}
outp_smry_ls <- X@c_SpecificResults@a_SpecificShareable@shareable_outp_ls
saveRDS(outp_smry_ls, 
        paste0(outp_smry_ls$path_to_write_to_1L_chr, "/I_ALL_OUTPUT_.RDS"))
```

```{r}
# write_analyses(input_params_ls) # Secondary analyses component

```

