---
title: "specific"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{specific}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, warning=FALSE, message=FALSE}
library(specific)
```
The [ready4 framework model modules](https://www.ready4-dev.com/docs/framework/implementation/modularity/) in `specific` are designed to make it easier to specify and assess potential solutions inverse problems as part of the [ready4 youth mental health economic model](https://www.ready4-dev.com/docs/model/) (or any other model developed with the [ready4 framework](https://www.ready4-dev.com)). This development version of the `specific` package has been made available as part of the process of testing and documenting the package. Currently there is one vignette describing how to use modules contained within `specific`:

- [Undertake An Exploratory Modelling Analysis](V_01.html)
